Update Meeting: 15-10-2021

### 2021-10-19 analysis/update_meeting_15_10_2021.Rmd
add table description of coordinate impact

@@

>>>>

The table below gives the data in the plot above:

- `outcome_description` corresponds to the trait. 
- `PC` is the genetic PC. 
- `trait_couple_corr` is the correlation of `outcome_description` in couples. 
- `PC_couple_corr` is the correlation of `PC` in couples. 
- `trait_PC_corr` is the correlation of `outcome_description` with `PC`.
-  `corr_due_to_confounding` corresponds to the formula: `cor(X,PC)^2*cor(PC_i,PC_p)`.

@@

The table below gives the data in the plot above:

- `outcome_description` corresponds to the trait. 
- `coordinate` is the coordiante (North: 129 or East: 130). 
- `trait_couple_corr` is the correlation of `outcome_description` in couples. 
- `coordinate_couple_corr` is the correlation of `coordinate` in couples. 
- `trait_coordinate_corr` is the correlation of `outcome_description` with `coordinate`.
-  `corr_due_to_confounding` corresponds to the formula: `cor(X,coord)^2*cor(coord_i,coord_p)`.
